ICM testing

### 2023-10-04 Scripts/Paper_1.Rmd
Including Lotka output in tunning
This includes the mx/lx nat mort, and fecundity vectors used to get the r value, so this can be used to get at other metrics we might want.

   back.tunes <- tune.sim(years,
                          tuner = 'f',
                           n.steps = 100, step.size = 0.2,
                           abund.ts = vpa.abund,
                           mat.age = age.mat,
                           nm = -(log(1-prop.nat.mort)),
                           w.age = weight.age,
                           ages = ages,
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.end,
                           pop.model = 'exponential',
                           direction='backwards')

@@

   for.tunes   <- tune.sim(years,
                           tuner='f',
                           n.steps =100, step.size =0.2,
                           abund.ts = vpa.abund,
                           mat.age = age.mat,
                           nm = -(log(1-prop.nat.mort)),
                           w.age = weight.age,
                           ages = ages,
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.start,
                           pop.model = 'exponential',
                           direction= 'forwards')

>>>>

   back.tunes <- tune.sim(years,
                          tuner = 'f',
                           n.steps = 250, step.size = 0.2,
                           abund.ts = vpa.abund,
                           mat.age = age.mat,
                           nm = -(log(1-prop.nat.mort)),
                           w.age = weight.age,
                           ages = ages,
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.end,
                           pop.model = 'exponential',
                           direction='backwards')

@@

   for.tunes   <- tune.sim(years,
                           tuner='f',
                           n.steps =250, step.size =0.2,
                           abund.ts = vpa.abund,
                           mat.age = age.mat,
                           nm = -(log(1-prop.nat.mort)),
                           w.age = weight.age,
                           ages = ages,
                           rems = rem$rem,
                           fecund = mx,
                           N.init = N.start,
                           pop.model = 'exponential',
                           direction= 'forwards')
